% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{setspace}
\usepackage{fullpage}
\usepackage{hyperref}

\setlength{\textwidth}{5.4in} % set width of text portion
\voffset = -45pt
\textheight = 850pt

\oddsidemargin -.5in
\evensidemargin -.4in
\textwidth=6.0in
\itemsep=0in
\parsep=0in


\smallskip
\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\Large\bf Aiswarya P. Kolisetty}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width 7.3in height 1.3pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{email: aiswarya.kolisetty@students.olin.edu}
\moveleft.5\hoffset\centerline{website: www.aiswaryakolisetty.com}
 \moveleft.5\hoffset\centerline{C: (630) 853 8334}



\section{EDUCATION}  {\bf Franklin W. Olin College of Engineering} in Needham, MA \hfill May 2013\\
  \hspace*{7mm}{B.S. in Electrical \& Computer Engineering (ECE)} \\ 
  \hspace*{7mm}Full-tuition scholarship,  GPA 3.47\\
\hspace*{7mm}{\small{{Technical:} Comp Architecture, A/D Communications, Circuits, Signals \& Systems}}\\
	{\bf University of Illinois} in Urbana-Champaign, IL (Study Away)   \hfill Jan - May 2012\



\vspace*{3mm}


\section{EXPERIENCE}

{\bf User Experience Intern} - Waltham, MA \hfill           February 2013 - May 2013\
\smallskip
	\begin{itemize}  \itemsep -4pt %reduce space between items
	
	 \item Working with a stealth-mode startup to enhance the usability of their software. 
	\item  Conducting user tests and developing for their front-end web UI. 
	\end{itemize}



	{\bf Tesla Motors, Systems Test Intern (Model S)} - Palo Alto, CA \hfill            May - August 2012\
\smallskip
	\begin{itemize}  \itemsep -4pt %reduce space between items
	
	 \item Automated user behavior tests, saving 2+ hrs of manual testing on a firmware release.
	\item Validated firmware that will be in production cars: reported bugs, simulated faults.
	\item Kickstarted upgrade of the Model S testing buck to start-of-production version
	\end{itemize}


{\bf Tesla Motors, Touchscreen User Experience} (side project) - Palo Alto, CA \hfill            July 2012\
\smallskip
	\begin{itemize}  \itemsep -4pt %reduce space between items
	
	 \item Redesigned sections of the Central Display on the Model S with wireframes.  
\item Conducted usability studies with testers, iterated designs, and presented 4 ideas to UI manager. 
	\end{itemize}
 

	{ \bf IMEC Vehicle Design Intern} - Leuven, Belgium \hfill            June - August 2011\
\smallskip
	\begin{itemize}  \itemsep -4pt %reduce space between items
	
	 \item Concepted {\emph{Aura}} - concept vehicle for daily commute in European cities. 
	\item  Human powered with electric-assist; focuses on personalization, sustainability, social sharing.  
\item Designed exteriors, interiors, and engineering specs.  Fabrication planned for June 2012.
	\end{itemize}



	{\bf CQS GroepT Racing Team (Electronics) } - Leuven, Belgium \hfill            June - September 2011 \
	\smallskip
	\begin{itemize}  \itemsep -4pt %reduce space between items
			
                 \item Wireless communication between electric car {\textit{Odyssee}} and pitlane for real-time data collection.  
	\item Improved reliability and got exposed to using RS-232 Serial Communication with Xbee.
	\item Brought modularity to team's data-analyzing Java software, now easily adds/tracks sensors.
	\end{itemize}
	


         {\bf Personality Psychology Research Assistant} - Olin College \hfill            June 2010 - May 2011 \
	\smallskip
                 \begin{itemize}  \itemsep -4pt %reduce space between items
			
                 \item Co-author of paper on Borderline Personality Disorder in psych journal  {\small{(June - August 2010)}}; 
%	\item How the experience of mixed emotions predicts good outcomes {\small{(Sept - Dec 2010)}}; 
%	\item How the physical human body affects lifestyle with age {\small{(January-May 2011)}}
                 \end{itemize}

\vspace*{3mm}

\section{PROJECTS \\}


{ \bf Suffrage iPhone App } (Working Title)  \hfill            January - May 2013\ 
	\smallskip
	\begin{itemize}  \itemsep -4pt %reduce space between items
	
	 \item An app for people to share the meaning of voting and elections their life. 
	\item Currently building the iOS app; hope to have a working prototype by May. 
	\end{itemize}

{ \bf Myndr iPhone App: An Aid for Alzheimer's}   \hfill            September 2012 - May 2013\ 
	\smallskip
	\begin{itemize}  \itemsep -4pt %reduce space between items
	
	 \item Testing \& codesigning for an iOS app with Alzheimer's patients and caretakers.  
	\end{itemize}


{ \bf Zimba, a Water Purifier in India}   \hfill            September 2012 - January 2013\ 
	\smallskip
	\begin{itemize}  \itemsep -4pt %reduce space between items
	
	 \item Product redesign of Zimba, a water chlorinator that gives drinking water to the poor
	\end{itemize}

%{\bf Business Technical Consulting} - Urbana, IL \hfill            January - May 2012\
%\smallskip
%	\begin{itemize}  \itemsep -4pt %reduce space between items
%	
%	 \item Tripled online web traffic for start-up founders of WhatFitsMe.com. 
%	\item Established the website functionality and redesigned the UI and interaction flows.  
%	\end{itemize}


{\bf Human Factors Interface Design} \hfill September - December 2011\
\smallskip
	\begin{itemize}  \itemsep -4pt %reduce space between items 
		
	\item Designed UI of {\emph {BOWtie}}, a cross-registration course planning tool.
	\item Process: paper prototypes and usability tests; Prototype: HTML5, CSS, JavaScript. %\href{http://hfid.olin.edu/sa2012/s_engr3220-ajax/prototype_v2/home.html}{Here} is the prototype.
	\end{itemize}


%{\bf User-Oriented Collaborative Design} \hfill January - May 2011\
%\smallskip
%	\begin{itemize}  \itemsep -4pt %reduce space between items 
%		
%	\item Ideated \& co-designed with  people in the body modification subculture in Boston. 
%\item  Designed final product {\emph{EnhancInk}} to fit the needs \& lives of our tattoo users. 
%	\end{itemize}

{\bf 	Principles of Engineering} \hfill September - December 2010\
\smallskip
	\begin{itemize}  \itemsep -4pt %reduce space between items 
		
	\item Built a mechatronic automatic lock cracker that takes finds the correct combination and cracks it open any MasterLock.  Featured in \emph{Wired, ASME magazine}.
	\end{itemize}
\vspace*{3mm}

\section{SKILLS}  HTML/CSS, JavaScript,  Adobe CS, Objective-C, Python, C, Java, mySQL, MATLAB
%\section {INTERESTS}  Photography, Frisbee, Society of Women Engineers ({\emph{New England Collegiate Representative}})
\end{document}




